Moral Foundations of U.S. Political News Organizations

### 2020-08-05 manuscript/Partisan Media Manuscript.Rmd

#setwd('C:/Users/kayla/Documents/GitHub/Will-Pilot/manuscript')
nsim = 100

@@

# Eliminate Duplicates
exp1 <- na.omit(exp1)

@@

# Loop over the DVs and create values 
# This saves the difference between groups
r = 1
for(DV in DVs){
  for(group in groups){
    data = subset(exp1, PartisanLean==group)
    f = as.formula(paste(DV,'~1', sep=''))
    bs = bootstrap_values(f,data,nsim)
    table1[r, 1] = DV
    if(group==0){
      table1[r, 2] = mean(bs$mean)
      table1[r, 3] = mean(bs$sd)
      ncon = length(na.omit(data[[DV]]))
      table1[r, 9] = quantile(bs$mean, 0.025)
      table1[r, 10] = quantile(bs$mean, 0.975)
    }
    if(group==1){
      table1[r, 4] = mean(bs$mean)
      table1[r, 5] = mean(bs$sd)
      nlib = length(na.omit(data[[DV]]))
      table1[r, 11] = quantile(bs$mean, 0.025)
      table1[r, 12] = quantile(bs$mean, 0.975)
    }
  }
  mdiff = d.ind.t(m1 = table1[r,2], m2 = table1[r,3], 
                sd1 = table1[r,4], sd2 = table1[r,5],
                n1 = ncon, 
                n2 = nlib, 
                a = .05)
  table1[r, 6] = mdiff$d
  table1[r, 7] = mdiff$dlow
  table1[r, 8] = mdiff$dhigh
  r = r + 1
}
```

@@

@@

#subset with Event=='gs'
exp2 <- subset(exp2, Event == "gs")
```

```{r bootstrap-study-2-kavanaugh-hearings}
exp2 <- import("exp2_merged data_LIWC.csv")
colnames(exp2)[1:5] = c('Source', 'URL', 'Text', 'Event', 'PartisanLean')

#subset with Event=='kav'

@@

>>>>

#setwd('C:/Users/kayla/Documents/GitHub/Will-Pilot/manuscript')
nsim = 10

@@

# Eliminate Missing Data
exp1 <- na.omit(exp1)

@@

# Loop over the DVs and create values 
# This saves the difference between groups
r = 1
for(DV in DVs){
  for(group in groups){
    data = subset(exp1, PartisanLean==group) #data name
    f = as.formula(paste(DV,'~1', sep=''))
    bs = bootstrap_values(f,data,nsim)
    table1[r, 1] = DV
    if(group==0){
      table1[r, 2] = mean(bs$mean) #table name all the way down 
      table1[r, 3] = mean(bs$sd)
      ncon = length(na.omit(data[[DV]]))
      table1[r, 9] = quantile(bs$mean, 0.025)
      table1[r, 10] = quantile(bs$mean, 0.975)
    }
    if(group==1){
      table1[r, 4] = mean(bs$mean)
      table1[r, 5] = mean(bs$sd)
      nlib = length(na.omit(data[[DV]]))
      table1[r, 11] = quantile(bs$mean, 0.025)
      table1[r, 12] = quantile(bs$mean, 0.975)
    }
  }
  mdiff = d.ind.t(m1 = table1[r,2], m2 = table1[r,4], 
                sd1 = table1[r,3], sd2 = table1[r,5],
                n1 = ncon, 
                n2 = nlib, 
                a = .05)
  table1[r, 6] = mdiff$d
  table1[r, 7] = mdiff$dlow
  table1[r, 8] = mdiff$dhigh
  r = r + 1
}
```

@@

- put notes here, I fixed the code

@@

# Eliminate Missing Data

#subset with Event=='gs'
exp2_gs <- subset(exp2, Event == "gs")

@@

```{r bootstrap-study-2-kavanaugh-hearings}

#subset with Event=='kav'
exp2_kav ... 
```
